---
title: "Homework Assignment #1"
---


**Your Name**:Jiwon MOk
**Your G Number**: G01096224


In this homework assignment we will be focusing on data analysis and visualization with the `tidyverse` 


# Load Packages and Data

The `R` code chunk below will load the `tidyverse` packages as well as an `auto_claims` data set.



```{r}
library(tidyverse)
auto_claims <- read_rds("~/https:/github.com/mason-sp22-cds101/ideal-jiwon/auto_claims.rds")
```



The `auto_claims` data contains information on auto accident claims processed by an insurance company in the western part of the United States.

Each row represents a claim made by a customer and includes customer demographics, their policy characteristics, monthly premium, vehicle information, claim amount, and [customer lifetime value](https://en.wikipedia.org/wiki/Customer_lifetime_value)


```{r}
auto_claims
```

# Problem 1

Write one expression using dplyr functions and the %>% operator to create the summary table below, and arrange it based on the customer state.

This table contains the number of claims, maximum claim amount (total_claim_amount variable), and minimum customer lifetime value by customer_state and months_since_last_claim binned into 12 month categories.

**Hint**: You will need to create the `month_category` variable using `cut_width()` before you calculate the summaries by groups.
```{r}
library(dplyr)
auto_claims %>%
 mutate(month_category=cut_width(monthly_premium, width =12, boundary=0))%>%
  group_by(customer_state) %>%
  summarize(n_claims = total_claim_amount, avg_claim_amunt = mean(total_claim_amount), min_customer_lifetime_val = min(customer_lifetime_value), month_category)
```


# Problem 2

Write one expression using dplyr functions and the %>% operator to create the summary table below.

This table contains the average, median, and maximum values of total_claim_amount by vehicle_class.


```{r}
auto_claims %>%
  group_by(vehicle_class)%>%
  summarise(min_amount = min(total_claim_amount), median_amount = median(total_claim_amount), max_amount = max(total_claim_amount), avg_amount = mean(total_claim_amount))
```




# Problem 3

Use ggplot to create the data visualization below. Please use alpha = 0.25 and color = '#006633' within your geom function to match the points below.


```{r}
ggplot(auto_claims, aes(x= customer_lifetime_value, y= total_claim_amount))+
  geom_point(alpha=0.25, color = '#006633')+
  facet_wrap(~ vehicle_size + sales_channel)+
  labs(title = "Total Claim Amount vs Customer Lifetime Value by sales channel and Vehicle size")

```


# Problem 4

Use ggplot to create the data visualization below.Width value is 0.07 and the aplha value is 0.1


```{r}
ggplot(auto_claims, aes(x=sales_channel, y=total_claim_amount, fill = sales_channel))+
  geom_violin(alpha = 0.1, width=0.07, trim=FALSE)+geom_jitter(alpha=0.1, position = position_jitter(width=0.1))
  labs(title = "violin plot of total claim amount by sales channel")
```


# Problem 5

Use `ggplot` to create the data visualization below. The number of bins in the histogram should be set to 15.


```{r}
ggplot(auto_claims, aes(x=total_claim_amount, fill=customer_state))+
  geom_histogram(bins=15, color = 'white')+
  facet_wrap(~customer_state)+
  labs( y= 'Proportion of Customers', x = 'Total Claim Amount')
```




# Problem 6

Use `ggplot` to create the data visualization below.


```{r}
ggplot(auto_claims, aes(y= highest_education, fill = vehicle_class))+
  geom_bar(position="fill")+
  labs(title = 'Vehicle Size Ownership by Highest Education')+
  labs(x = 'Proportion of Customers')

```



--- End of Assignment ---