---
title: "Homework Assignment #1"
---


**Your Name**:
**Your G Number**:


In this homework assignment we will be focusing on data analysis and visualization with the `tidyverse` 


# Load Packages and Data

The `R` code chunk below will load the `tidyverse` packages as well as an `auto_claims` data set.



```{r}
library(tidyverse)

auto_claims <- read_rds('C:/RDataFiles/auto_claims.rds')
```



The `auto_claims` data contains information on auto accident claims processed by an insurance company in the western part of the United States.

Each row represents a claim made by a customer and includes customer demographics, their policy characteristics, monthly premium, vehicle information, claim amount, and [customer lifetime value](https://en.wikipedia.org/wiki/Customer_lifetime_value)


```{r}
auto_claims
```



# Problem 1

Write one expression using dplyr functions and the %>% operator to create the summary table below, and arrange it based on the customer state.

This table contains the number of claims, maximum claim amount (total_claim_amount variable), and minimum customer lifetime value by customer_state and months_since_last_claim binned into 12 month categories.

**Hint**: You will need to create the `month_category` variable using `cut_width()` before you calculate the summaries by groups.


```{r}






```



# Problem 2

Write one expression using dplyr functions and the %>% operator to create the summary table below.

This table contains the average, median, and maximum values of total_claim_amount by vehicle_class.


```{r}



  
```




# Problem 3

Use ggplot to create the data visualization below. Please use alpha = 0.25 and color = '#006633' within your geom function to match the points below.


```{r}







```




# Problem 4

Use ggplot to create the data visualization below.Width value is 0.07 and the aplha value is 0.1


```{r}






```




# Problem 5

Use `ggplot` to create the data visualization below. The number of bins in the histogram should be set to 15.


```{r}





```




# Problem 6

Use `ggplot` to create the data visualization below.


```{r}



```



--- End of Assignment ---